### 2018-03-23 Sections/network_algorithms.tex
Latin quotes done
Crypto, CV
Bit of indexing

\begin{table*}[!htb]
	\begin{tabular}{|c|c|c|c|}
		\hline
  		\rowcolor{Dandelion} Algorithm & Description & Complexity class & Scaling \\
  		\hline
  		\hline
  		\rowcolor{LimeGreen} Breadth-first-search & Explore all vertices in a graph & \textbf{P} & $O(|V|+|E|)$ \\
  		\hline
  		\rowcolor{LimeGreen} Depth-first-search & (same as above) & \textbf{P} & $O(|V|+|E|)$ \\
		\hline
  		\rowcolor{LimeGreen} Shortest-path (Dijkstra) & Find the shortest route between two nodes & \textbf{P} & $O(|V|^2)$ \\
  		\rowcolor{LimeGreen} & in a directed graph & &  \\
  		  		\hline
		\rowcolor{LimeGreen} Shortest-path (\textit{A*}) & (same as above) & \textbf{P} & (varying) \\
  		  		\hline
		\rowcolor{LimeGreen} Single-source shortest path & Find the shortest paths from a given node to & \textbf{P} & $O(|V|\cdot |E|)$\\
  		\rowcolor{LimeGreen} & \textit{all} other nodes & & \\
 		\hline
		\rowcolor{LimeGreen} Minimum spanning tree & Find a spanning tree of a graph that minimises & \textbf{P} & $O(|E|\text{log}|V|)$ \\
  		\rowcolor{LimeGreen} & the total of the edge weights & & \\
  		\hline
  		\rowcolor{LimeGreen} Minimum cost flow & Minimise total costs in a network &  \textbf{P} & $O(|V|\text{log}|V|(|E|$\\
  		\rowcolor{LimeGreen} (Orlin) & with a specified amount of flow& & $+|V|\text{log}|V|))$ \\
  		\hline
  		\rowcolor{LimeGreen} Maximum flow & Maximise flow in a network, regardless of costs & \textbf{P} & $O(|E|\cdot c_\text{max})$ \\
  		\rowcolor{LimeGreen} (Ford-Fulkerson) & & & \\
  		\hline
  		\rowcolor{Lavender} Multi-commodity flow & Same as maximum flow, but generalised to & \textbf{NP}-complete & ? \\
  		\rowcolor{Lavender} & arbitrary numbers of users & (exactly), & \\
  		\rowcolor{Lavender} & & \textbf{P} (approximation & \\
  		\rowcolor{Lavender} & & using heuristics) & \\
  		\hline
  		\rowcolor{Lavender} Vehicle routing problem & Generalises the shortest-path algorithm to multiple & \textbf{NP}-complete & ? \\
  		\rowcolor{Lavender} & users, with distinct sources and destinations & & \\ 
  		\hline
  		\rowcolor{Lavender} Vehicle rescheduling problem & Same as above but with dynamically changing costs & \textbf{NP}-complete & ? \\
    	\hline
	\end{tabular}
	\caption{Summary of some important network algorithms and their complexities. The \textbf{NP}-complete algorithms are not believed to have efficient classical algorithms, and their exact scaling is not well understood.} \label{tab:net_alg_sum} \index{Network algorithms}\index{Breadth-first-search algorithm}\index{Depth-first-search algorithm}\index{Shortest-path algorithm}\index{Single-source shortest path algorithm}\index{Minimum spanning tree algorithm}\index{Minimum cost flow algorithm}\index{Maximum flow algorithm}\index{Multi-commodity flow algorithm}\index{Vehicle routing problem}\index{Vehicle rescheduling problem}
\end{table*}

@@

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function DijkstraShortestPath($G$,$A$,$B$):
\begin{enumerate}
	\item currentNode = $A$
    \item tentativeDistances[$A$] = 0
    \item tentativeDistances[others] = $\infty$
    \item nodesVisited[$A$] = True
    \item nodesVisited[others] = False
    \item loopStart:
    \item neighbours = currentNode.neighbourhood
    \item nodesVisited[neighbours] = True
    \item for(n$\in$neighbours) \{
    \setlength{\itemindent}{0.2in}
    \item newTentativeDist = \\ min(tentativeDistances[currentNode] \\+ edgeWeight[currentNode,n],\\
        tentativeDistances[n])\\
    \item nodesVisited[currentNode] = True
    \setlength{\itemindent}{0in}
    \item \}
    \item if(nodesVisited[$B$] = True) \{
    \setlength{\itemindent}{0.2in}
	\item return(tentativeDistances[$B$])
	\item $\Box$
    \setlength{\itemindent}{0in}
    \item \}
	\item currentNode = \\
	tentativeDistances[unvisitedNodes].\\
	nodeWithSmallest()
	\item goto(loop)
    \item $\Box$
\end{enumerate}}}}
\caption{Dijkstra's original shortest-path algorithm for finding the lowest weight path through a graph, $G$, between two vertices, $A$ (source) and $B$ (destination). The algorithm has $O(|V|^2)$ runtime (in \textbf{P}). \comment{Fix me}} \label{alg:dijkstra}\index{Shortest-path algorithm}
\end{table}

>>>>

\begin{table*}[!htb]
	\begin{tabular}{|c|c|c|c|}
		\hline
  		\rowcolor{Dandelion} Algorithm & Description & Complexity class & Scaling \\
  		\hline
  		\hline
  		\rowcolor{LimeGreen} Breadth-first-search & Explore all vertices in a graph & \textbf{P} & $O(|V|+|E|)$ \\
  		\hline
  		\rowcolor{LimeGreen} Depth-first-search & (same as above) & \textbf{P} & $O(|V|+|E|)$ \\
		\hline
  		\rowcolor{LimeGreen} Shortest-path (Dijkstra) & Find the shortest route between two nodes & \textbf{P} & $O(|V|^2)$ \\
  		\rowcolor{LimeGreen} & in a directed graph & &  \\
  		  		\hline
		\rowcolor{LimeGreen} Shortest-path (\textit{A*}) & (same as above) & \textbf{P} & (varying) \\
  		  		\hline
		\rowcolor{LimeGreen} Single-source shortest path & Find the shortest paths from a given node to & \textbf{P} & $O(|V|\cdot |E|)$\\
  		\rowcolor{LimeGreen} & \textit{all} other nodes & & \\
 		\hline
		\rowcolor{LimeGreen} Minimum spanning tree & Find a spanning tree of a graph that minimises & \textbf{P} & $O(|E|\text{log}|V|)$ \\
  		\rowcolor{LimeGreen} & the total of the edge weights & & \\
  		\hline
  		\rowcolor{LimeGreen} Minimum cost flow & Minimise total costs in a network &  \textbf{P} & $O(|V|\text{log}|V|(|E|$\\
  		\rowcolor{LimeGreen} (Orlin) & with a specified amount of flow& & $+|V|\text{log}|V|))$ \\
  		\hline
  		\rowcolor{LimeGreen} Maximum flow & Maximise flow in a network, regardless of costs & \textbf{P} & $O(|E|\cdot c_\text{max})$ \\
  		\rowcolor{LimeGreen} (Ford-Fulkerson) & & & \\
  		\hline
  		\rowcolor{Lavender} Multi-commodity flow & Same as maximum flow, but generalised to & \textbf{NP}-complete & ? \\
  		\rowcolor{Lavender} & arbitrary numbers of users & (exactly), & \\
  		\rowcolor{Lavender} & & \textbf{P} (approximation & \\
  		\rowcolor{Lavender} & & using heuristics) & \\
  		\hline
  		\rowcolor{Lavender} Vehicle routing problem & Generalises the shortest-path algorithm to multiple & \textbf{NP}-complete & ? \\
  		\rowcolor{Lavender} & users, with distinct sources and destinations & & \\ 
  		\hline
  		\rowcolor{Lavender} Vehicle rescheduling problem & Same as above but with dynamically changing costs & \textbf{NP}-complete & ? \\
    	\hline
	\end{tabular}
	\caption{Summary of some important network algorithms and their complexities. The \textbf{NP}-complete algorithms are not believed to have efficient classical algorithms, and their exact scaling is not well understood.} \label{tab:net_alg_sum} \index{Network algorithms}\index{Breadth-first-search (BFS) algorithm}\index{Depth-first-search (DFS) algorithm}\index{Shortest-path algorithm}\index{Single-source shortest path algorithm}\index{Minimum spanning tree algorithm}\index{Minimum cost flow algorithm}\index{Maximum flow algorithm}\index{Multi-commodity flow algorithm}\index{Vehicle routing problem}\index{Vehicle rescheduling problem}
\end{table*}

@@

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function DijkstraShortestPath($G$,$A$,$B$):
\begin{enumerate}
	\item currentNode = $A$
    \item tentativeDistances[$A$] = 0
    \item tentativeDistances[others] = $\infty$
    \item nodesVisited[$A$] = True
    \item nodesVisited[others] = False
    \item loopStart:
    \item neighbours = currentNode.neighbourhood
    \item nodesVisited[neighbours] = True
    \item for(n$\in$neighbours) \{
    \setlength{\itemindent}{0.2in}
    \item newTentativeDist = \\ min(tentativeDistances[currentNode] \\+ edgeWeight[currentNode,n],\\
        tentativeDistances[n])\\
    \item nodesVisited[currentNode] = True
    \setlength{\itemindent}{0in}
    \item \}
    \item if(nodesVisited[$B$] = True) \{
    \setlength{\itemindent}{0.2in}
	\item return(tentativeDistances[$B$])
	\item $\Box$
    \setlength{\itemindent}{0in}
    \item \}
	\item currentNode = \\
	tentativeDistances[unvisitedNodes].\\
	nodeWithSmallest()
	\item goto(loop)
    \item $\Box$
\end{enumerate}}}}
\caption{Dijkstra's original shortest-path algorithm for finding the lowest weight path through a graph, $G$, between two vertices, $A$ (source) and $B$ (destination). The algorithm has $O(|V|^2)$ runtime (in \textbf{P}).} \label{alg:dijkstra}\index{Shortest-path algorithm}
\end{table}

### 2018-03-23 Sections/optical_encoding_of_quantum_information.tex
tiny
minor
Bit of indexing

\begin{figure}[!htb]
\includegraphics[width=0.2\textwidth]{photonic_qubit_encodings}
\caption{Three approaches to encoding a single qubit using a single photon, via a superposition across two spatial ($A$ and $B$), polarisation ($V$ and $H$) or temporal ($t$ and \mbox{$t+\tau$}) modes.} \label{fig:photonic_qubit_encodings}
\end{figure}

@@

@@

When encoding information optically, we needn't restrict ourselves to photon-number states. We also have a lot of flexibility to encode information in phase-space using continuous variable (CV) states, where phase and amplitude relations encode quantum information \cite{bib:CahillGlauber69}.

>>>>

\begin{figure}[!htb]
\includegraphics[width=0.15\textwidth]{photonic_qubit_encodings}
\caption{Three approaches to encoding a single qubit using a single photon, via a superposition across two spatial ($A$ and $B$), polarisation ($V$ and $H$) or temporal ($t$ and \mbox{$t+\tau$}) modes.} \label{fig:photonic_qubit_encodings}
\end{figure}

@@

\comment{Advantages and disadvantages of different types of encoding.}

@@

When encoding information optically, we needn't restrict ourselves to photon-number states. We also have a lot of flexibility to encode information in phase-space using continuous-variable (CV) states, where phase and amplitude relations encode quantum information \cite{bib:CahillGlauber69}.

### 2018-03-23 Sections/physical_architectures_for_quantum_computing.tex
Bit of indexing

The amplitudes $\gamma_{S,T}$ are given by,\index{Boson-sampling configuration amplitudes}
\begin{align}
	\gamma_{S,T} = \frac{\text{Per}(U_{S,T})}{\sqrt{S_1!\dots S_m! T_1!\dots T_m!}},
\end{align}
and the associated configuration probabilities by\index{Boson-sampling configuration probabilities},
\begin{align}
	P_{S,T} &= |\gamma_{S,T}|^2 \nonumber \\
	&= \frac{|\text{Per}(U_{S,T})|^2}{S_1!\dots S_m! T_1!\dots T_m!}
\end{align}
where $\text{Per}(\cdot)$ denotes the matrix permanent, and $U_{S,T}$ is a sub-matrix of $U$ -- the transfer matrix\index{Transfer matrix} associated with the particular input-to-output sample configuration -- obtained by taking $S_i$ copies of the $i$th row, and $T_j$ copies of the $j$th column of the linear optics unitary matrix $U$. For the purposes of the original complexity proof, the unitary is chosen randomly from the Haar-measure\footnote{The Haar-measure generalises the notion of a uniform distribution to higher-dimensional topologies than the real numbers, in this instance to the $\text{SU}(n)$ group.}\index{Haar measure}, although it remains an open question as to what is the full class of unitaries that yield computationally hard problems.

@@

%
% Continuous Variables (CV)
%

\subsection{Continuous variables (CV)} \label{sec:CV_QC} \index{Continuous variable quantum computation}

Until now we have focussed on optical systems where quantum information is encoded into discrete variables\index{Discrete variables}, such as photon-number and polarisation. However, quantum states of light can also be considered in terms of continuous variables (CVs)\index{Continuous variables} in phase-space\index{Phase-space}.

>>>>

The amplitudes $\gamma_{S,T}$ are given by,\index{Boson-sampling configuration amplitudes}
\begin{align}
	\gamma_{S,T} = \frac{\text{Per}(U_{S,T})}{\sqrt{S_1!\dots S_m! T_1!\dots T_m!}},
\end{align}
and the associated configuration probabilities by,
\begin{align}
	P_{S,T} &= |\gamma_{S,T}|^2 \nonumber \\
	&= \frac{|\text{Per}(U_{S,T})|^2}{S_1!\dots S_m! T_1!\dots T_m!}
\end{align}
where $\text{Per}(\cdot)$ denotes the matrix permanent, and $U_{S,T}$ is a sub-matrix of $U$ -- the transfer matrix\index{Transfer matrix} associated with the particular input-to-output sample configuration -- obtained by taking $S_i$ copies of the $i$th row, and $T_j$ copies of the $j$th column of the linear optics unitary matrix $U$. For the purposes of the original complexity proof, the unitary is chosen randomly from the Haar-measure\footnote{The Haar-measure generalises the notion of a uniform distribution to higher-dimensional topologies than the real numbers, in this instance to the $\text{SU}(n)$ group.}\index{Haar measure}, although it remains an open question as to what is the full class of unitaries that yield computationally hard problems.

@@

%
% Continuous-Variables (CV)
%

\subsection{Continuous-variables (CV)} \label{sec:CV_QC} \index{Continuous-variable quantum computation}

Until now we have focussed on optical systems where quantum information is encoded into discrete variables\index{Discrete variables}, such as photon-number and polarisation. However, quantum states of light can also be considered in terms of continuous-variables (CVs)\index{Continuous-variables} in phase-space\index{Phase-space}.

### 2018-03-23 Sections/quantum_algorithms.tex
minor
tiny
Bit of indexing

The QFT matrix simply contains coefficients taken from the discrete Fourier transform (DFT)\index{Discrete Fourier transform}. Specifically, the \mbox{$N\times N$} QFT matrix has elements,
\begin{align}
\hat{QFT}_{j,k} = \frac{1}{\sqrt{N}} \omega^{(j-1)(k-1)},	
\end{align}
where,
\begin{align}
\omega = e^{\frac{2\pi i}{N}},	
\end{align}
is a complex root of unity. In matrix form the $N$-dimensional QFT is therefore,
\begin{align}
\hat{QFT}_N = \frac{1}{\sqrt{N}} \left(\begin{matrix}
  1 & 1 & 1 & \dots & 1\\
  1 & \omega & \omega^2 & \dots & \omega^{N-1} \\
  1 & \omega^2 & \omega^4 & \dots & \omega^{2(N-1)} \\
  \vdots & \vdots & \vdots & \ddots & \vdots \\
  1 & \omega^{N-1} & \omega^{2(N-1)} &\dots &\omega^{(N-1)(N-1)}
\end{matrix}\right),
\end{align}
which is symmetric, \mbox{$\hat{QFT}=\hat{QFT}^\top$}. Note that all matrix elements are phases with magnitude $1/\sqrt{N}$,
\begin{align}
	|\hat{QFT}_{i,j}|=\frac{1}{\sqrt{N}}\,\,\forall\, i,j.
\end{align}

Equivalently, in terms of basis state transformations this implements the map,
\begin{align}
	\hat{QFT} \ket{j} \to \frac{1}{\sqrt{N}}\sum_{k=0}^{N-1} \omega^{jk}\ket{k},
\end{align}
on the $N$ basis states.

@@

The algorithm for this is baked from several ingredients. To implement phase-estimation with $n$ bits of precision, we require:
\begin{itemize}
	\item An $n$-qubit Hadamard transform, $\hat{H}^{\otimes n}$\index{Hadamard transform}.
	\item $n$ controlled-$\hat{U}$s\footnote{Any unitary has a coherently controlled unitary equivalent, of the form $\hat{U}_\text{controlled} = \ket{0}\bra{0}\otimes \hat{\mathbb{I}} + \ket{1}\bra{1}\otimes\hat{U}$. These always have an efficient circuit construction, given $\hat{U}$.}.
	\item An $n$-qubit inverse QFT\index{Quantum Fourier transform}, $\hat{QFT}_n^\dag$ (Sec.~\ref{sec:QFT_alg}).
\end{itemize}

@@

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function PhaseEstimation($\hat{U}$, $\ket\psi$):
\begin{enumerate}
	\item For unitary $\hat{U}$ with eigenvector $\ket\psi$, apply the circuit below.
	\item The register of qubits at the output to the QFT encodes $2^n\theta$ in binary representation.
	\item $\Box$
\end{enumerate}
\begin{align}
\Qcircuit @C=1em @R=1.6em {
    \lstick{\ket{0}} & \gate{\hat{H}} & \qw &\qw & \dots && \ctrl{3} & \multigate{2}{\hat{QFT}^{-1}} & \meter \\
    \lstick{\vdots} & \gate{\hat{H}} & \qw &\qw & \dots & & \qw & \ghost{\hat{QFT}^{-1}} & \meter \\
    \lstick{\ket{0}} & \gate{\hat{H}} & \ctrl{1} &\qw & \dots && \qw & \ghost{\hat{QFT}^{-1}} & \meter \\
    \lstick{\ket{\psi}} & \qw & \gate{\hat{U}^{2^0}} &\qw & \dots & &\gate{\hat{U}^{2^{n-1}}} & \qw & \qw \\
} \nonumber
\end{align}
}}}
\caption{Quantum phase-estimation algorithm.} \label{alg:q_phase_est}
\end{table}

@@

\subsection{Optimisation, satisfiability \& \textbf{NP}-complete problems}\index{Optimisation problems}\index{\textbf{NP}-complete problems}\index{Satisfiability problems}

@@

Such \textbf{NP}-complete algorithms can be quadratically enhanced in runtime using Grover's algorithm. To see this, note that all \textbf{NP}-complete problems can be efficiently mapped to one another with polynomial resource overhead (see Fig.~\ref{fig:complexity_classes}). Thus, we can restrict ourselves to considering the satisfiability problems\index{Satisfiability problems} discussed above -- the archetypal \textbf{NP}-complete problems. An example of the 3-\textsc{SAT} problem\index{3-\textsc{SAT} problem}, which is \textbf{NP}-complete, is shown in Fig.~\ref{fig:3SAT}.

\begin{figure}[!htb]
\includegraphics[width=0.3\textwidth]{3SAT}
\caption{Digital circuit for an instance of the 3-\textsc{SAT} problem, with 4 clauses acting on input variables $\{x_i\}$. Each of the OR gates is input with some combination of 3 of the input bits or their compliments (i.e with a NOT gate). Each of these is referred to as a `clause', of which there are 4 in this example, but could be any number in general. The final AND gate requires that all clauses be simultaneously satisfied in order to yield a final output of `1'. The goal of the problem is to find an input bit-string $x$ that yields an output of `1'. In general, this may require exhaustively searching over the entire space of input states via brute-force, which exhibits time-complexity exponential in the length of the bit-string. This problem is proven to be \textbf{NP}-complete. Note that the similarly-defined 2-\textsc{SAT}\index{2-\textsc{SAT} problem} problem (i.e clauses each contain 2 input bits) is \textbf{P}, making 3-\textsc{SAT} the simplest model to consider in the study of \textbf{NP}-complete problems.} \label{fig:3SAT}	
\end{figure}

@@

Calculating Betti numbers exactly is known to be \textbf{PSPACE}-complete\index{\textbf{PSPACE}-complete}\footnote{\textbf{PSPACE} is the complexity class of problems requiring polynomial memory with unbounded runtime, a class that is not classically efficient.}, and the best-known classical approximation algorithm has exponential runtime,
\begin{align}
O(2^n \mathrm{log}(1/\delta)),
\end{align}
for accuracy $\delta$ on $n$ data-points.

@@

>>>>

The QFT matrix simply contains coefficients taken from the discrete Fourier transform (DFT)\index{Discrete Fourier transform}. Specifically, the \mbox{$N\times N$} QFT matrix has elements,
\begin{align}
\hat{\text{QFT}}_{j,k} = \frac{1}{\sqrt{N}} \omega^{(j-1)(k-1)},	
\end{align}
where,
\begin{align}
\omega = e^{\frac{2\pi i}{N}},	
\end{align}
is a complex root of unity. In matrix form the $N$-dimensional QFT is therefore,
\begin{align}
\hat{\text{QFT}}_N = \frac{1}{\sqrt{N}} \left(\begin{matrix}
  1 & 1 & 1 & \dots & 1\\
  1 & \omega & \omega^2 & \dots & \omega^{N-1} \\
  1 & \omega^2 & \omega^4 & \dots & \omega^{2(N-1)} \\
  \vdots & \vdots & \vdots & \ddots & \vdots \\
  1 & \omega^{N-1} & \omega^{2(N-1)} &\dots &\omega^{(N-1)(N-1)}
\end{matrix}\right),
\end{align}
which is symmetric, \mbox{$\hat{\text{QFT}}=\hat{\text{QFT}}^\top$}. Note that all matrix elements are phases with magnitude $1/\sqrt{N}$,
\begin{align}
	|\hat{\text{QFT}}_{i,j}|=\frac{1}{\sqrt{N}}\,\,\forall\, i,j.
\end{align}

Equivalently, in terms of basis state transformations this implements the map,
\begin{align}
	\hat{\text{QFT}} \ket{j} \to \frac{1}{\sqrt{N}}\sum_{k=0}^{N-1} \omega^{jk}\ket{k},
\end{align}
on the $N$ basis states.

@@

The algorithm for this is baked from several ingredients. To implement phase-estimation with $n$ bits of precision, we require:
\begin{itemize}
	\item An $n$-qubit Hadamard transform, $\hat{H}^{\otimes n}$\index{Hadamard transform}.
	\item $n$ controlled-$\hat{U}$s\footnote{Any unitary has a coherently controlled unitary equivalent, of the form $\hat{U}_\text{controlled} = \ket{0}\bra{0}\otimes \hat{\mathbb{I}} + \ket{1}\bra{1}\otimes\hat{U}$. These always have an efficient circuit construction, given $\hat{U}$.}.
	\item An $n$-qubit inverse quantum Fourier transform\index{Quantum Fourier transform}, $\hat{\text{QFT}}_n^\dag$ (Sec.~\ref{sec:QFT_alg}).
\end{itemize}

@@

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function PhaseEstimation($\hat{U}$, $\ket\psi$):
\begin{enumerate}
	\item For unitary $\hat{U}$ with eigenvector $\ket\psi$, apply the circuit below.
	\item The register of qubits at the output to the QFT encodes $2^n\theta$ in binary representation.
	\item $\Box$
\end{enumerate}
\begin{align}
\Qcircuit @C=1em @R=1.6em {
    \lstick{\ket{0}} & \gate{\hat{H}} & \qw &\qw & \dots && \ctrl{3} & \multigate{2}{\hat{QFT}^\dag} & \meter \\
    \lstick{\vdots} & \gate{\hat{H}} & \qw &\qw & \dots & & \qw & \ghost{\hat{QFT}^\dag} & \meter \\
    \lstick{\ket{0}} & \gate{\hat{H}} & \ctrl{1} &\qw & \dots && \qw & \ghost{\hat{QFT}^\dag} & \meter \\
    \lstick{\ket{\psi}} & \qw & \gate{\hat{U}^{2^0}} &\qw & \dots & &\gate{\hat{U}^{2^{n-1}}} & \qw & \qw \\
} \nonumber
\end{align}
}}}
\caption{Quantum phase-estimation algorithm.} \label{alg:q_phase_est}
\end{table}

@@

\subsection{Optimisation, satisfiability \& \textbf{NP}-complete problems}\index{Optimisation problems}\index{\textbf{NP}-complete}\index{Satisfiability problems}

@@

Such \textbf{NP}-complete algorithms can be quadratically enhanced in runtime using Grover's algorithm. To see this, note that all \textbf{NP}-complete problems can be efficiently mapped to one another with polynomial resource overhead (see Fig.~\ref{fig:complexity_classes}). Thus, we can restrict ourselves to considering the satisfiability problems\index{Satisfiability problems} discussed above -- the archetypal \textbf{NP}-complete problems. An example of the 3-\textsc{SAT} problem\index{3-SAT problem}, which is \textbf{NP}-complete, is shown in Fig.~\ref{fig:3SAT}.

\begin{figure}[!htb]
\includegraphics[width=0.3\textwidth]{3SAT}
\caption{Digital circuit for an instance of the 3-\textsc{SAT} problem, with 4 clauses acting on input variables $\{x_i\}$. Each of the OR gates is input with some combination of 3 of the input bits or their compliments (i.e with a NOT gate). Each of these is referred to as a `clause', of which there are 4 in this example, but could be any number in general. The final AND gate requires that all clauses be simultaneously satisfied in order to yield a final output of `1'. The goal of the problem is to find an input bit-string $x$ that yields an output of `1'. In general, this may require exhaustively searching over the entire space of input states via brute-force, which exhibits time-complexity exponential in the length of the bit-string. This problem is proven to be \textbf{NP}-complete. Note that the similarly-defined 2-\textsc{SAT}\index{2-SAT problem} problem (i.e clauses each contain 2 input bits) is \textbf{P}, making 3-\textsc{SAT} the simplest model to consider in the study of \textbf{NP}-complete problems.} \label{fig:3SAT}	
\end{figure}

@@

Calculating Betti numbers exactly is known to be \textbf{PSPACE}-complete\index{\textbf{PSPACE}-complete}\footnote{\textbf{PSPACE} is the complexity class of problems requiring polynomial memory with unbounded runtime, a class that is not classically efficient.}, and the best-known classical approximation algorithm has exponential runtime,
\begin{align}
O(2^n \text{log}(1/\delta)),
\end{align}
for accuracy $\delta$ on $n$ data-points.

@@

\comment{Finish mathematical details}

### 2018-03-23 Sections/the_quantum_space_race.tex
Bit of indexing

Involving ground-based quantum network nodes is not an inherent problem as 80\% of the atmosphere by mass is located within the first 12km in altitude, yielding low effective thickness of the atmosphere\index{Effective atmospheric thickness}. This effective thickness of course changes with the azimuth of the satellite in the sky. Near the horizon the line-of-sight\index{Line-of-sight} between satellite and ground-station is far greater than when the satellite is directly overhead. The light trajectory beyond this effective thickness regime effectively passes through vacuum with attenuation\index{Attenuation} limited only by diffraction\index{Diffraction}. Thus, when directly overhead, a satellite-to-ground\index{Satellite-to-ground} channel is more favourable in terms of signal attenuation than long-distance ground-to-ground\index{Ground-to-ground} channels.

@@

\begin{figure}[!htb]
	\includegraphics[width=0.47\textwidth]{satellite_constellation}
	\caption{Satellite constellation network for bypassing line-of-sight constraints in long-distance quantum communication. Neighbouring satellites connect via line-of-sight in space, and there are a sufficient number of satellites to enable global coverage such that all points on the Earth's surface are visible to at least one satellite at any given time, giving them indirect quantum access to any other point on the globe. In this example, entanglement swapping between satellites shares a Bell-pair between Columbia and Tasmania, enabling the teleportation of cocaine from Bogot{\'a} to Peter's holiday home.} \label{fig:sat_constellation}\index{Satellite constellation}
\end{figure}

>>>>

Involving ground-based quantum network nodes is not an inherent problem as 80\% of the atmosphere by mass is located within the first 12km in altitude, yielding low effective thickness of the atmosphere\index{Effective atmospheric thickness}. This effective thickness of course changes with the azimuth of the satellite in the sky. Near the horizon the line-of-sight\index{Line-of-sight} between satellite and ground-station is far greater than when the satellite is directly overhead. The light trajectory beyond this effective thickness regime effectively passes through vacuum with attenuation\index{Photon loss} limited only by diffraction\index{Diffraction}. Thus, when directly overhead, a satellite-to-ground\index{Satellite-to-ground} channel is more favourable in terms of signal attenuation than long-distance ground-to-ground\index{Ground-to-ground} channels.

@@

\begin{figure}[!htb]
	\includegraphics[width=0.47\textwidth]{satellite_constellation}
	\caption{Satellite constellation network for bypassing line-of-sight constraints in long-distance quantum communication. Neighbouring satellites connect via line-of-sight in space, and there are a sufficient number of satellites to enable global coverage such that all points on the Earth's surface are visible to at least one satellite at any given time, giving them indirect quantum access to any other point on the globe. In this simple example, entanglement swapping between satellites shares a Bell-pair between Columbia and Tasmania, enabling the teleportation of certain Columbian products\index{Benzoylmethylecgonine} from Bogot{\'a} to the dance parties at Rohde's holiday home.\index{Pablo Escobar}} \label{fig:sat_constellation}\index{Satellite constellation}
\end{figure}
